---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickGraph

<!-- badges: start -->
<!-- badges: end -->

The goal of quickGraph is to create a functions that helps researchers 
quickly fit a model on a data set and visualize the data alongside the model. 
Additionally the plot will provide basic statistics including the model function, 
F-statistic and adjusted R-square. Currently, the quickGraph library only has 
one function, plotLinearModel, which fits and visualize simple linear model. 

## Installation

quickGraph is not yet on CRAN. It can be downloaded from this repository using 
the following R command: 

``` r
devtools::install_github("Glenn032787/quickGraph")
```

## Usage

This is basic usage of the function of plotLinearModel.

```
@param data Data set in form of tibble that is being plotted (Must have at least three valid row)
@param x Column in data that is the x axis of plot (Name of column X should be character (in quotes) and data in column x should be numeric)
@param y Column in data that is the y axis of plot (Name of column y should be character (in quotes) and data in column y should be numeric)

@return ggplot2 scatter plot with of data points from column x and y and visualization of the fitted linear model with simple linear function as the title and adjusted r-squared and F-statistic as subtitle

USAGE: plotLinearModel(data, x, y)

```
The output is a ggplot object with data points from column x and y in data and a line representing the simple linear model that is fitted from of those data. The title of the ggplot object is the simple linear function and the subtitle is the adjusted R-squared value and F-statistic of the linear model. The data in the x and y columns in data must be numeric. Rows containing NA in column x and y are not included in model fitting and in plot. Data should have at least 3 numeric rows so that the linear model can be calculated. Note that the data set must be a tibble rather than a data frame. Also note that the column names for x and y should be character data type (inside quotation). 

## Example

This is a basic example which shows you how to fit a simple linear model onto the
mpg and disp column in mtcars data set. This allows for researchers to quickly 
visualize the relationship between mpg and disp in mtcars data set. 

```{r example}
library(quickGraph)

mt_car.tb <- tibble::as_tibble(mtcars)

plotLinearModel(mt_car.tb, "mpg", "disp")
```
